Automated verification of stand-alone solar photovoltaic systems

### 2018-11-13 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r2.tex
minor corrections
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

The voltage and the current at the maximum power point tracking (MPPT), can be expressed by \eqref{eq:Vmfinal}, \eqref{eq:Imfinal}, and \eqref{eq:Pm} \cite{Saloux}. %These equations are used to calculate the key cell parameters at the maximum power point as function cell temperature and parameters from the manufacturer's data-sheet.
\begin{equation}
\label{eq:Vmfinal}
V_{m}=\dfrac{aNk_{B}T}{q} ln \left( \dfrac{aNk_{B}T}{qI_{0}} \dfrac{I_{sc}}{V_{oc}}  \right) 
\end{equation}

\begin{equation}
\label{eq:Imfinal}
I_{m} = I_{ph} + I_{0} - \dfrac{aNk_{B}T}{q} \left( \dfrac{I_{sc}}{V_{oc}} \right)  
\end{equation}

\begin{equation}
\label{eq:Pm}
P_{m} = V_{m} I_{m}
\end{equation}

>>>>

The voltage and the current at the maximum power point tracking (MPPT), can be expressed by \eqref{eq:Vmfinal}, \eqref{eq:Imfinal}, and \eqref{eq:Pm} \cite{Saloux}. %These equations are used to calculate the key cell parameters at the maximum power point as function cell temperature and parameters from the manufacturer's data-sheet.
\begin{equation}
\label{eq:Vmfinal}
V_{m}=\dfrac{aNk_{B}T}{q} ln \left( \dfrac{aNk_{B}T}{qI_{0}} \dfrac{I_{sc}}{V_{oc}}  \right). 
\end{equation}

\begin{equation}
\label{eq:Imfinal}
I_{m} = I_{ph} + I_{0} - \dfrac{aNk_{B}T}{q} \left( \dfrac{I_{sc}}{V_{oc}} \right).  
\end{equation}

\begin{equation}
\label{eq:Pm}
P_{m} = V_{m} I_{m}.
\end{equation}
